\documentclass[a4paper]{article} 
\input{head}
\usepackage{pdfpages}
\usepackage{placeins}
\usepackage{incgraph,tikz}
\begin{document}

%-------------------------------
%	TITLE SECTION
%-------------------------------

\pagebreak
\fancyhead[C]{}
\hrule \medskip % Upper rule
\begin{minipage}{0.295\textwidth} 
\raggedright
\footnotesize
Halil İbrahim Ceylan - 390709073  halilibrahimceylan2@posta.mu.edu.tr\hfill\\   
Fatih Emre YILDIZ - 180702004  fatihemreyildiz@posta.mu.edu.tr\hfill\\
\end{minipage}
\begin{minipage}{0.4\textwidth} 
\centering 
\large 
Final Project\\ 
\normalsize 
CENG 3521: Data Mining\\ 
\end{minipage}
\begin{minipage}{0.295\textwidth} 
\raggedleft
\today\hfill\\
\end{minipage}
\medskip\hrule 
\bigskip

%-------------------------------
%	CONTENTS
%-------------------------------
\bigskip
\bigskip

{\centering\LARGE\bfseries
  Project's Topic\par
}
\medskip
{\centering\large
  Electronic Sports - League of Legends\par
}
\bigskip
\bigskip

{\centering\LARGE\bfseries
  Project's Goal\par
}
\medskip
{\centering\large
  Try to guess the winner team\par
}
\bigskip
\bigskip

{\centering\LARGE\bfseries
  Project's Description\par
}
\medskip
{\centering\large
  We are going to use almost every data in the game. We don't know which parameter will be really effective to guess the end of the game. Our most known parameters are The gold which teams earn during the game, towers, inhibitors, wards, monsters killed for both teams, wards replacement, firstblood firstower and so on. We will explain the parameters better on our report. Our dataset is this: https://www.kaggle.com/gyejr95/league-of-legends-challenger-ranked-games2020 There are almost 200.000 games. We do not know about which loss function we are going to use. We will decide it later on while we are doing the project.\par
}
\bigskip
\bigskip

{\centering\LARGE\bfseries
  Abstraction\par
}
\medskip
{\centering\large
Electronic sports (eSports) is a type of sport competition which uses video games.
It's popularity has increased in recent years, has gradually become a part of modern sports.
Electronic sports, which has achieved progress since the early 2000s,
It has great potential to show a similar development as modern sports in a shorter time.

Recently, one of the popular games in the field of eSports has become Multiplayer Online Battle Arena (MOBA). MOBA type games currently occupy a large place in the eSports industry. The most popular game of the genre is "League of Legends"  debuted on 2009. League of Legends, which currently has 30 million players worldwide and is claimed to be the most played game,
It has hundreds of thousands of players and millions of viewers.

In this study, with the data of the one of the popular game of today League of Legends,  we have we aimed to predict which team will win. \par}
\bigskip
\pagebreak


\setcounter{section}{0}
\centering
\section{Introduction}

\subsection{Description Of The Game}
League of Legends is a Multiplayer Online Battle Arena game. Which is shorten as MOBA.
\medskip
  
It is a team-based strategy game. There are five players for each team. To win the game, teams have to destroy the other's base which is called Nexus. To win the game players have to take down enemies, get the vision, earn gold, get stronger, and take down towers as they battle their way to victory.
\medskip
    
On the playground, there are many parameters as, towers, minions, inhibitors, jungle camps, wards etc.
\medskip

From each team's Nexus, Minions will spawn till the end of the game and go through the three lanes. The three lanes are known as top lane, mid lane, and bot lane. In all three lanes, there are turrets and they will attack enemy champions and minions. Each lane has three turrets and one inhibitor, Each Inhibitor is protected by a Turret. When an Inhibitor destroyed, super minions will spawn in that lane for several minutes, then it will re-spawn and Super Minions will stop spawning. 

\medskip

In between the lanes, there is the jungle. There are neutral monsters in the jungle. There are two important monsters in the jungle these are Dragon and Baron. which gives advantages to the teams when destroyed. 

\medskip 

Each of these objects returns players as experience and gold. With experience players get higher levels, with gold player gets more stronger, can buy wards and get vision over the map. With more vision, teams can control the map and the enemy team.

\medskip 

Thus, almost every data in our data-set can affect the end of the game.

\medskip 

To inspect the data and try to predict the end of the game we have selected to use Data Preprocessing, Linear Classification, Neural Network-based Classification and Clustering.

\medskip

\subsection{Dataset}
We got our data on the website called kaggle. We have 50 columns. They were.

\medskip

\textbf{gameId:} 
Unique ID to identify the game.

\textbf{gameDuraton:} 
Game Duration in seconds.

\textbf{blueWins-redWins:} 
Winner Team

\textbf{blueFirstBlood-redFirstBlood:} 
Team who has the first score.

\textbf{blueFirstTower-redFirstTower:} 
Team who has destroyed the first tower.

\textbf{blueFirstBaron-redFirstBaron:} 
Team who has got the first Baron.

\textbf{blueFirstDragon-redFirstDragon:} 
Team who has got the first Dragon.

\textbf{blueFirstInhibitor-redFirstInhibitor:} 
Team who has got the first Inhibitor.

\textbf{blueDragonKills-redDragonKills:} 
Number of the Dragons killed by teams.

\textbf{blueBaronKills-redBaronKills:} 
Number of the Barons killed by teams.

\textbf{blueTowerKills-redTowerKills:} 
Number of the Towers taken by teams.

\textbf{blueInhibitorKills-redInhibitorKills:} 
Number of the Inhibitors taken by teams.

\textbf{blueWardPlaced-redWardPlaced:} 
Number of the Wards placed by teams.

\textbf{blueWardkills-redWardkills:} 
Number of the Wards killed by teams.

\textbf{blueKills-redKills:} 
Number of the Scores taken by teams.

\textbf{blueDeath-redDeath:} 
Number of the Scores given by teams.

\textbf{blueAssist-redAssist:} 
Number of the Assistance taken by teams.

\textbf{blueChampionDamageDealt-redChampionDamageDealt:} 
Damage Dealt by champions to enemy team.

\textbf{blueTotalGold-redTotalGold:} 
Number of the Gold gained by teams.

\textbf{blueTotalMinionKills-redTotalMinionKills:} 
Number of the Minions killed by teams.

\textbf{blueTotalLevel-redTotalLevel:} 
Total Level of the teams.

\textbf{blueAvgLevel-redAvgLevel:} 
Average Level of the teams.

\textbf{blueJungleMinionKills-redJungleMinionKills:} 
Number of the Jungle Minion killed by teams.

\textbf{blueKillingSpree-redKillingSpree:} 
Number of total kills for a champion without getting died.

\textbf{blueTotalHeal-redTotalHeal:} 
Number of heal gained for the teams.

\textbf{blueObjectDamageDealt-redObjectDamageDealt:} 
Damage Dealt by champions to objects.

 
\bigskip
 

\pagebreak

\section{Data Preprocessing}

In this section, we have looked at our data, Since we have huge amount of data we did some pre-processing to make our data more suitable for the tasks. We have applied Sampling and Feature Subset Selection.

\subsection{Sampling}

Sampling is the selecting the certain data to analyze.

\bigskip 

In a game, If a player disconnects from the game and His/Her team doesn't want to play the game anymore, they can start voting to surrender. If the majority of the team doesn't want to play the game and votes for it. They can give up and lose the game by voting.
This affects our data in a bad way. In our dataset, some games are ended by voting. This made noise in our dataset. To avoid that we have deleted games that ended before 20 minutes. It gave us a more suitable dataset to work on. 

\subsection{Feature Subset Selection}

Feature Subset Selection is a way to reduce the dimension of the data by deleting the columns that we have. We have applied it to the Redundant Features and Irrelevant Features.

\bigskip 

\subsubsection{Redundant Features}

Redundant Features are the duplicated data in the dataset. 

\medskip

Since we have data for both teams some of our columns are related to each other. These columns represent the binary data for the first happened in the game. For example, the column 'redFirstBlood' is 1, It means that the Red team got the first score in the game, then 'blueFirstBlood' can not be other than 0. There are few conditions like these, these are 'redWins', 'redFirstInhibitor', 'redFirstBaron', 'redFirstDragon', 'redFirstTower'.


\medskip

2 columns are related to other columns. These are 'redAvgLevel', 'blueAvgLevel' represents the Average level of the teams. Since we have other columns that are multiplied by the team's Average Level with the number of player '5' for both teams 'redTotalLevel', 'blueTotalLevel'. We have deleted the columns related to the average levels of the teams.



\bigskip 

\subsubsection{Irrelevant  Features}

Irrelevant Features doesn't contain any information for our tasks.

\medskip

In this case there is only one column that doesn't affect the end of the game which is 'gameId'. 'gameId' is the unique data to identify the game.


\bigskip 

\subsection{Standardization}
Also we applied Standardization to our dataset. We used MinMaxScaler class from scikit learn. It transforms features by scaling each feature to a given range. We have scaled all the features between zero and one.


\subsection{Result}

Before Data preprocessing section we had 50 columns of dataset. We have examined every column. 
After we have applied the data preprocessing techniques, we reduced features to 41 without losing any information. 
\pagebreak

%------------------------------------------------

\end{document}